### 2013-01-10 edupar-13/410.tex
410.tex: compressed/fuzzed "terminal irony" description.

\item Robust code often requires a different structure
than a ``usually works'' solution.
The most straightforward way for an exiting task to
convey its exit status to its parent is for it to
\x{malloc()} an exit-status blob and enqueue it for
later processing by the parent.
However, this design suffers from a ``terminal irony'':
a program wishing to exit,
which will free up kernel memory,
is unable to do so if kernel memory has been exhausted.

>>>>

\item Robust code often requires a different structure
than a ``usually works'' solution.
It is easy to write task-exit code which
needs to allocate memory in order to notify its
parent that it has exited.
However, such designs suffer from ``terminal irony'':
a program wishing to exit,
which would free up kernel memory,
is unable to do so if kernel memory has been exhausted.
